A theorical-practical approach to manifold learning

### 2018-11-06 DimReduction/Mds/Documentation/Article_mds.tex
Adding conclusions to Mds documentation

Some of the approximations in these types of methods assume that the data that
is being analyzed does not exploit all the dimensionality of the space where
is defined. Due to this fact, another description of the goal that the
dimensionality reduction techniques have is related to find a meaningful low
dimensional structure that is hidden in a multidimentional structure.
\cite{dimension}

@@

One example of a manifold learning algorithm is called multidimensional
scaling \cite{mds}, this method addresses the problem by trying to find a low
dimensional distance matrix that is as close as possible to a multidimensional
version that encodes the relationship between the points in the original space.
Then the algorithm uses the founded matrix to build a correspondent configuration
of points in a low dimentional space that will act as a less complicated
representation of the original dataset.

@@

    As mentioned before, one of the goals of this work is to create a theorical
    development of the multidimentional scaling algorithm. This section shows a
    detail explanation of the therical aspects of the method taking \cite{proof}
    as base point.

@@

The method described in the previuos section was tested with 3 dimensional
manifolds in order to allow the visualization of the intial manifold and be able
to compare the quality of the resulting solution. Figure \ref{swiss} shows
a swiss roll dataset that was used as the multidimentional manifold. Figure
\ref{swiss_res} shows the result of the devolped method.

@@

@@

    \begin{equation*}
        \begin{aligned}
            Tr(B) &= T(A^tA)\\
                  &= \sum_{i=1}^n (A^tA)_{ii}\\
                  &= \sum_{i=1}^n \sum_{j=1}^n A_{ij}^t A_{ji}\\
                  &= \sum_{i=1}^n \sum_{j=1}^n A_{ji} A_{ji}\\
                  &= \sum_{i=1}^n \sum_{j=1}^n A_{ji}^2 \\
                  &= \sum_{i=1}^n \sum_{j=1}^n A_{ij}^2 \\
                  &= \lVert A \rVert^2
        \end{aligned}
    \end{equation*}

>>>>

Some of the approximations in these types of methods assume that the data that
is being analyzed does not exploit all the dimensionality of the space where
is defined. Due to this fact, another description of the goal that the
dimensionality reduction techniques have is related to find a meaningful low
dimensional structure that is hidden in a multidimensional structure.
\cite{dimension}

@@

One example of a manifold learning algorithm is called multidimensional
scaling \cite{mds}, this method addresses the problem by trying to find a low
dimensional distance matrix that is as close as possible to a multidimensional
version that encodes the relationship between the points in the original space.
Then the algorithm uses the founded matrix to build a correspondent configuration
of points in a low dimensional space that will act as a less complicated
representation of the original dataset.

@@

    As mentioned before, one of the goals of this work is to create a theorical
    development of the multidimensional scaling algorithm. This section shows a
    detail explanation of the therical aspects of the method taking \cite{proof}
    as base point.

@@

The method described in the previuos section was tested with 3 dimensional
manifolds in order to allow the visualization of the intial manifold and be able
to compare the quality of the resulting solution. Figure \ref{swiss} shows
a swiss roll dataset that was used as the multidimensional manifold. Figure
\ref{swiss_res} shows the result of the devolped method.

@@

In this work a theorical and practical development of the multidimensional
scaling method was permed. During the process it was found that what seemed like
a fairly complicated problem, can be simplified to simple matrix operations
with the help of some concepts from linear algebra. Thanks to that theorical
framework, the construction of a relatively simple algorithm that can detect
low dimensional manifolds embedded in multidimensional spaces was possible.
Finally the results shown that this technique has the ability to make
contributions to the analysis proces of multidimensional datasets by
simplifying its features but preserving the intrinsic structure.

@@

    \begin{equation*}
        \begin{aligned}
            Tr(B) &= T(A^tA)\\
                  &= \sum_{i=1}^n (A^tA)_{ii}\\
                  &= \sum_{i=1}^n \sum_{j=1}^n A_{ij}^t A_{ji}\\
                  &= \sum_{i=1}^n \sum_{j=1}^n A_{ji} A_{ji}\\
                  &= \sum_{i=1}^n \sum_{j=1}^n A_{ji}^2 \\
                  &= \sum_{i=1}^n \sum_{j=1}^n A_{ij}^2 = \lVert A \rVert^2 \\
        \end{aligned}
    \end{equation*}
